Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-05-29 output/manuscript.tex
fix equations

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{mathtools}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\usepackage[inkscapeformat=pdf,inkscapelatex=false]{svg}
\newcommand{\bm}[1]{\boldsymbol{#1}}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{american}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}

@@

Here we briefly provide the details about these TWAS methods that are necessary to explain our regression framework later (see the referenced articles for more information).
In the following, we refer to \(\mathbf{y}\) as a vector of traits for \(n\) individuals that is centered for convenience (so that no intercept is necessary);
\(\mathbf{\tilde{t}}_l = \sum_{a \in \mathrm{model}_l} w_{a}^{l} X_{a}\) is the gene's predicted expression for all individuals in tissue \(l\), \(X_a\) is the genotype of SNP \(a\) and \(w_{a}\) its weight in the tissue prediction model \(l\);
and \(\mathbf{t}_l\) is the standardized version of \(\mathbf{\tilde{t}}_l\) with mean equal to zero and standard deviation equal to one.

@@

where \(\mathbf{T}\) is a matrix with \(p\) columns \(\mathbf{t}_l\),
\(\hat{g}_l\) is the estimated effect size for the predicted gene expression in tissue \(l\) (and thus \(\mathbf{\hat{g}}\) is a vector with \(p\) estimated effect sizes \(\hat{g}_l\)),
and \(\mathbf{e}\) are the error terms with variance \(\sigma_{e}^{2}\).
Given the high correlation between predicted expression values for a gene across different tissues, MultiXcan uses the principal components (PCs) of \(\mathbf{T}\) to avoid collinearity issues.
S-MultiXcan derives the joint regression estimates (effect sizes and their variances) in Equation (\ref{eq:multixcan}) using the marginal estimates from S-PrediXcan in Equation (\ref{eq:spredixcan}).
Under the null hypothesis of no association, \(\mathbf{\hat{g}}^{\top} \frac{\mathbf{T}^{\top}\mathbf{T}}{\sigma_{e}^{2}} \mathbf{\hat{g}} \sim \chi_{p}^{2}\), and therefore the significance of the association in S-MultiXcan is estimated with

\begin{equation}
\begin{split}
\frac{\mathbf{\hat{g}}^{\top} (\mathbf{T}^{\top}\mathbf{T}) \mathbf{\hat{g}}}{\sigma_{e}^{2}} & \approx \bm{\hat{\gamma}}^{\top} \frac{\sqrt{n-1}}{\sigma_{\epsilon}} \left(\frac{\mathbf{T}^{\top} \mathbf{T}}{n-1}\right)^{-1} \frac{\sqrt{n-1}}{\sigma_{\epsilon}} \bm{\hat{\gamma}} \\
 & = \mathbf{\hat{z}}^{\top} Cor(\mathbf{T})^{-1} \mathbf{\hat{z}},
\end{split}
\label{eq:smultixcan}\end{equation}

where \(\mathbf{\hat{z}}\) is a vector with \(p\) \(z\)-scores (Equation (\ref{eq:spredixcan})) for each tissue available for the gene,
and \(Cor(\mathbf{T})\) is the autocorrelation matrix of \(\mathbf{T}\).
Since \(\mathbf{T}^{\top}\mathbf{T}\) is singular for many genes, S-MultiXcan computes the pseudo-inverse \(Cor(\mathbf{T})^{+}\) using the \(k\) top PCs, and thus \(\mathbf{\hat{z}}^{\top} Cor(\mathbf{T})^{+} \mathbf{\hat{z}} \sim \chi_k^2\).
To arrive at this expression, S-MultiXcan uses the conservative approximation \(\sigma_{e}^{2} \approx \sigma_{\epsilon}^{2}\), that is, the variance of the error terms in the joint regression is approximately equal to the residual variance of the marginal regressions.
Another important point is that \(Cor(\mathbf{T})\) is estimated using a global genotype covariance matrix, whereas marginal \(\hat{z}_l\) in Equation (\ref{eq:spredixcan}) are approximated using tissue-specific genotype covariances.
Although S-MultiXcan yields highly concordant estimates compared with MultiXcan, results are not perfectly correlated across genes {[}\protect\hyperlink{ref-1FFzCXo1s}{24}{]}.
As we explain later, these differences are important for our LV-based regression model when computing the gene-gene correlation matrix.
We used S-MultiXcan results for our LV-based regression model and our cluster analyses of traits.

@@

\begin{equation}
\begin{split}
\frac{(\mathbf{T}_{i}^{\top} \mathbf{T}_{j})_{kl}}{n-1} & = Cor(\mathbf{t}_k^i, \mathbf{t}_l^j) \\
 & = \frac{ Cov(\mathbf{t}_k, \mathbf{t}_l) } { \sqrt{\widehat{\mathrm{var}}(\mathbf{t}_k) \widehat{\mathrm{var}}(\mathbf{t}_l)} } \\
 & = \frac{ Cov(\sum_{a \in \mathrm{model}_k} w_a^k X_a, \sum_{b \in \mathrm{model}_l} w_b^l X_b) }  {\sqrt{\widehat{\mathrm{var}}(\mathbf{t}_k) \widehat{\mathrm{var}}(\mathbf{t}_l)} } \\
 & = \frac{ \splitfrac{\sum_{a \in \mathrm{model}_k}{b \in \mathrm{model}_l}} w_a^k w_b^l Cov(X_a, X_b)} {\sqrt{\widehat{\mathrm{var}}(\mathbf{t}_k) \widehat{\mathrm{var}}(\mathbf{t}_l)} } \\
        & = \frac{ \splitfrac{\sum_{a \in \mathrm{model}_k}{b \in \mathrm{model}_l}} w_a^k w_b^l \Gamma_{ab}} {\sqrt{\widehat{\mathrm{var}}(\mathbf{t}_k) \widehat{\mathrm{var}}(\mathbf{t}_l)} },
\end{split}
\label{eq:reg:corr_genes}\end{equation}

where \(X_a\) is the genotype of SNP \(a\),
\(w_a^k\) is the weight of SNP \(a\) for gene expression prediction in the tissue model \(k\),
and \(\Gamma = \widehat{\mathrm{var}}(\mathbf{X}) = (\mathbf{X} - \mathbf{\bar{X}})^{\top} (\mathbf{X} - \mathbf{\bar{X}}) / (n-1)\) is the genotype covariance matrix using GTEx v8 as the reference panel, which is the same used in all TWAS methods described here.
The variance of the predicted expression values of gene \(i\) in tissue \(k\) is estimated as {[}\protect\hyperlink{ref-vLyTudUB}{99}{]}:

\begin{equation}
\begin{split}
\widehat{\mathrm{var}}(\mathbf{t}_k^i) & = (\mathbf{W}^k)^\top \Gamma^k \mathbf{W}^k \\
        & = \sum_{\splitfrac{a \in \mathrm{model}_k}{b \in \mathrm{model}_k}} w_a^k w_b^k \Gamma_{ab}^k.
\end{split}
\label{eq:reg:var_gene}\end{equation}

@@

\hypertarget{supplementary-material}{%
\subsection{Supplementary material}\label{supplementary-material}}

@@

\hypertarget{crispr-cas9}{%
\subsubsection{CRISPR-Cas9}\label{crispr-cas9}}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:fig1}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure1.png}
\caption{\textbf{EVOS Fluorescence Microscope Image Capture.}
A. HepG2\_lentiV2\_Ctrl with no-viral transduction.
B. HepG2\_lentiV2 with viral transduction.
Both no-viral transduction Control (A) and lentiviral transduction (B) HepG2 cells were stained with LipidSpot™488.}\label{fig:sup:crispr:fig1}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:fig2}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure2.png}
\caption{\textbf{Fluorescence-Activated Cell Sorting Gate Setting.}
A. HepG2\_UnStained WT.
B. HepG2\_lentiV2 with viral transduction stained with LipidSpot™488.
HepG2\_lentiV2 cells were FAC sorted, 20\% of GFP-High and 20\% of GFP-Low cell populations were collected.}\label{fig:sup:crispr:fig2}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:fig3}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure3.png}
\caption{\textbf{Verification of sgRNA cassette and lentiV2 transgene.}
A. 20nt sgRNA cassette was verified in lentiV2 transduced genomic DNA population, 163 bp PCR product obtained, while WT HepG2 didn't possess the cassette, thus, no PCR product.
B. lentiviral-specific transgene WPRE was verified in lentiV2 transduced genomic DNA population, while no transduced WT didn't have the transgene, therefore, no 173 bp PCR product observed.
For both panels A and B, 100 bp ladder was used in Lane 0.}\label{fig:sup:crispr:fig3}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:table1}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/table1.png}
\caption{}\label{fig:sup:crispr:table1}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:fig4}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure4.png}
\caption{\textbf{Illumina library generation.}
A. Construct for generating Illumina libraries.
B. Final Illumina library from HS DNA ---showed a single \textasciitilde285bp peak was generated.}\label{fig:sup:crispr:fig4}
}
\end{figure}

@@

\hypertarget{consensus-clustering-of-traits}{%
\subsubsection{Consensus clustering of traits}\label{consensus-clustering-of-traits}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{mathtools}
\usepackage{lmodern}
\usepackage{iftex}
\usepackage[legalpaper, left=0.5in, right=0.5in, top=1in, bottom=1in]{geometry}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\usepackage[inkscapeformat=pdf,inkscapelatex=false]{svg}
\newcommand{\bm}[1]{\boldsymbol{#1}}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{american}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}

@@

Here we briefly provide the details about these TWAS methods that are necessary to explain our regression framework later (see the referenced articles for more information).
In the following, we refer to \(\mathbf{y}\) as a vector of traits for \(n\) individuals that is centered for convenience (so that no intercept is necessary);
\(\tilde{\mathbf{t}}_l = \sum_{a \in \mathrm{model}_l} w_{a}^{l} X_{a}\) is the gene's predicted expression for all individuals in tissue \(l\), \(X_a\) is the genotype of SNP \(a\) and \(w_{a}\) its weight in the tissue prediction model \(l\);
and \(\mathbf{t}_l\) is the standardized version of \(\tilde{\mathbf{t}}_l\) with mean equal to zero and standard deviation equal to one.

@@

where \(\mathbf{T}\) is a matrix with \(p\) columns \(\mathbf{t}_l\),
\(\hat{g}_l\) is the estimated effect size for the predicted gene expression in tissue \(l\) (and thus \(\hat{\mathbf{g}}\) is a vector with \(p\) estimated effect sizes \(\hat{g}_l\)),
and \(\mathbf{e}\) are the error terms with variance \(\sigma_{e}^{2}\).
Given the high correlation between predicted expression values for a gene across different tissues, MultiXcan uses the principal components (PCs) of \(\mathbf{T}\) to avoid collinearity issues.
S-MultiXcan derives the joint regression estimates (effect sizes and their variances) in Equation (\ref{eq:multixcan}) using the marginal estimates from S-PrediXcan in Equation (\ref{eq:spredixcan}).
Under the null hypothesis of no association, \(\hat{\mathbf{g}}^{\top} \frac{\mathbf{T}^{\top}\mathbf{T}}{\sigma_{e}^{2}} \hat{\mathbf{g}} \sim \chi_{p}^{2}\), and therefore the significance of the association in S-MultiXcan is estimated with

\begin{equation}
\begin{split}
\frac{\hat{\mathbf{g}}^{\top} (\mathbf{T}^{\top}\mathbf{T}) \hat{\mathbf{g}}}{\sigma_{e}^{2}} & \approx \bm{\hat{\gamma}}^{\top} \frac{\sqrt{n-1}}{\sigma_{\epsilon}} \left(\frac{\mathbf{T}^{\top} \mathbf{T}}{n-1}\right)^{-1} \frac{\sqrt{n-1}}{\sigma_{\epsilon}} \bm{\hat{\gamma}} \\
 & = \hat{\mathbf{z}}^{\top} Cor(\mathbf{T})^{-1} \hat{\mathbf{z}},
\end{split}
\label{eq:smultixcan}\end{equation}

where \(\hat{\mathbf{z}}\) is a vector with \(p\) \(z\)-scores (Equation (\ref{eq:spredixcan})) for each tissue available for the gene,
and \(Cor(\mathbf{T})\) is the autocorrelation matrix of \(\mathbf{T}\).
Since \(\mathbf{T}^{\top}\mathbf{T}\) is singular for many genes, S-MultiXcan computes the pseudo-inverse \(Cor(\mathbf{T})^{+}\) using the \(k\) top PCs, and thus \(\hat{\mathbf{z}}^{\top} Cor(\mathbf{T})^{+} \hat{\mathbf{z}} \sim \chi_k^2\).
To arrive at this expression, S-MultiXcan uses the conservative approximation \(\sigma_{e}^{2} \approx \sigma_{\epsilon}^{2}\), that is, the variance of the error terms in the joint regression is approximately equal to the residual variance of the marginal regressions.
Another important point is that \(Cor(\mathbf{T})\) is estimated using a global genotype covariance matrix, whereas marginal \(\hat{z}_l\) in Equation (\ref{eq:spredixcan}) are approximated using tissue-specific genotype covariances.
Although S-MultiXcan yields highly concordant estimates compared with MultiXcan, results are not perfectly correlated across genes {[}\protect\hyperlink{ref-1FFzCXo1s}{24}{]}.
As we explain later, these differences are important for our LV-based regression model when computing the gene-gene correlation matrix.
We used S-MultiXcan results for our LV-based regression model and our cluster analyses of traits.

@@

\begin{equation}
\begin{split}
\frac{(\mathbf{T}_{i}^{\top} \mathbf{T}_{j})_{kl}}{n-1} & = Cor(\mathbf{t}_k^i, \mathbf{t}_l^j) \\
  & = \frac{ Cov(\mathbf{t}_k, \mathbf{t}_l) } { \sqrt{\widehat{\mathrm{var}}(\mathbf{t}_k) \widehat{\mathrm{var}}(\mathbf{t}_l)} } \\
  & = \frac{ Cov(\sum_{a \in \mathrm{model}_k} w_a^k X_a, \sum_{b \in \mathrm{model}_l} w_b^l X_b) }  {\sqrt{\widehat{\mathrm{var}}(\mathbf{t}_k) \widehat{\mathrm{var}}(\mathbf{t}_l)} } \\
  & = \frac{ \sum_{\substack{a \in \mathrm{model}_k \\ b \in \mathrm{model}_l}} w_a^k w_b^l Cov(X_a, X_b)} {\sqrt{\widehat{\mathrm{var}}(\mathbf{t}_k) \widehat{\mathrm{var}}(\mathbf{t}_l)} } \\
  & = \frac{ \sum_{\substack{a \in \mathrm{model}_k \\ b \in \mathrm{model}_l}} w_a^k w_b^l \Gamma_{ab}} {\sqrt{\widehat{\mathrm{var}}(\mathbf{t}_k) \widehat{\mathrm{var}}(\mathbf{t}_l)} },
\end{split}
\label{eq:reg:corr_genes}\end{equation}

where \(X_a\) is the genotype of SNP \(a\),
\(w_a^k\) is the weight of SNP \(a\) for gene expression prediction in the tissue model \(k\),
and \(\Gamma = \widehat{\mathrm{var}}(\mathbf{X}) = (\mathbf{X} - \bar{\mathbf{X}})^{\top} (\mathbf{X} - \bar{\mathbf{X}}) / (n-1)\) is the genotype covariance matrix using GTEx v8 as the reference panel, which is the same used in all TWAS methods described here.
The variance of the predicted expression values of gene \(i\) in tissue \(k\) is estimated as {[}\protect\hyperlink{ref-vLyTudUB}{99}{]}:

\begin{equation}
\begin{split}
\widehat{\mathrm{var}}(\mathbf{t}_k^i) & = (\mathbf{W}^k)^\top \Gamma^k \mathbf{W}^k \\
        & = \sum_{\substack{a \in \mathrm{model}_k \\ b \in \mathrm{model}_k}} w_a^k w_b^k \Gamma_{ab}^k.
\end{split}
\label{eq:reg:var_gene}\end{equation}

@@

\newpage
\hypertarget{supplementary-material}{%
\subsection{Supplementary material}\label{supplementary-material}}

@@

\clearpage
\hypertarget{crispr-cas9}{%
\subsubsection{CRISPR-Cas9}\label{crispr-cas9}}

@@

\begin{figure}[!h]
\hypertarget{fig:sup:crispr:fig1}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure1.png}
\caption{\textbf{EVOS Fluorescence Microscope Image Capture.}
A. HepG2\_lentiV2\_Ctrl with no-viral transduction.
B. HepG2\_lentiV2 with viral transduction.
Both no-viral transduction Control (A) and lentiviral transduction (B) HepG2 cells were stained with LipidSpot™488.}\label{fig:sup:crispr:fig1}
}
\end{figure}

@@

\begin{figure}[!h]
\hypertarget{fig:sup:crispr:fig2}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure2.png}
\caption{\textbf{Fluorescence-Activated Cell Sorting Gate Setting.}
A. HepG2\_UnStained WT.
B. HepG2\_lentiV2 with viral transduction stained with LipidSpot™488.
HepG2\_lentiV2 cells were FAC sorted, 20\% of GFP-High and 20\% of GFP-Low cell populations were collected.}\label{fig:sup:crispr:fig2}
}
\end{figure}

@@

\begin{figure}[!h]
\hypertarget{fig:sup:crispr:fig3}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure3.png}
\caption{\textbf{Verification of sgRNA cassette and lentiV2 transgene.}
A. 20nt sgRNA cassette was verified in lentiV2 transduced genomic DNA population, 163 bp PCR product obtained, while WT HepG2 didn't possess the cassette, thus, no PCR product.
B. lentiviral-specific transgene WPRE was verified in lentiV2 transduced genomic DNA population, while no transduced WT didn't have the transgene, therefore, no 173 bp PCR product observed.
For both panels A and B, 100 bp ladder was used in Lane 0.}\label{fig:sup:crispr:fig3}
}
\end{figure}

@@

\begin{figure}[!h]
\hypertarget{fig:sup:crispr:table1}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/table1.png}
\caption{}\label{fig:sup:crispr:table1}
}
\end{figure}

@@

\begin{figure}[!h]
\hypertarget{fig:sup:crispr:fig4}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure4.png}
\caption{\textbf{Illumina library generation.}
A. Construct for generating Illumina libraries.
B. Final Illumina library from HS DNA ---showed a single \textasciitilde285bp peak was generated.}\label{fig:sup:crispr:fig4}
}
\end{figure}

@@

\clearpage
\hypertarget{consensus-clustering-of-traits}{%
\subsubsection{Consensus clustering of traits}\label{consensus-clustering-of-traits}}
